---
title: "MIDA Work"
author: "David Koruna"
date: "4/28/2019"
output: pdf_document
---

```{r}
mida = read.csv("MIDA_4.2_Cleaned.csv")
midaneeded = mida[c(1,9,10,11,13,14,15,16,17,18,19,23)]
df = data.frame(c(1,2,3,4))
unclean = read.csv("MIDA_4.2.csv")
library(lsr)
library(corrplot)
library(ggplot2)
```


We believe that the positioning of the NA values in "fatlity" is not randomly distributed. Taking a look at the initial values,
```{r}
midaneeded[which(is.na(midaneeded$fatality)),]$hostlev
```

We can see that there is potential for "hostlev" to be influencing "fatality."

```{r}
qplot(midaneeded[which(is.na(midaneeded$fatality)),]$hostlev, geom = "histogram", binwidth = .5, xlab = "NA Fatality Hostility Levels")

```
This is shown in the histogram here. It seems that hostility levels involving "Use of Force" or higher are causing missing numbers of fatalities. 

We also want to take a look at correlation between categorical variables. I am choosing to compare "outcome," "settle," "fatality," hiact," "hostlev," "recip" and "ongo2010." We will use Cramer's V for our method of comparison. We will also have to remove NA values to do this analysis, as well as convert our booleans to binary variables.

```{r}
cramers = na.omit(midaneeded)
cramers$recip = as.integer(cramers$recip)
cramers$ongo2010 = as.integer(cramers$ongo2010)
cramers$outcome = as.numeric(cramers$outcome)
cramers$settle = as.numeric(cramers$settle)
cramercor = cor(cramers, use = "pairwise.complete.obs")
corrplot(cramercor, method = "color", type = "upper", addCoef.col = "black")
```

```{r}
midb$stabb = as.numeric(midb$stabb)
midbcor = midb[-c(4,5)]
midbcor = cor(midbcor, use = "pairwise.complete.obs")
corrplot(midbcor, method = "color", type = "upper", addCoef.col = "black")
```

Mention NA Bias on Fatality

Correlation between variables on the MIDA and MIDB dataset

Different Categorical Variables

